\subsection{Outlines from Stacey Shiflett}


%%%%%
\subsubsection{I Like It Like It Is}

\index[speaker]{Stacey Shiflett!Psalm 16:6 (I Like It Like It Is)}
\index[series]{Psalms (Stacey Shiflett)!Psalm 16:6 (I Like It Like It Is)}
\index[date]{2020/04/15!Psalm 16:6 (I Like It Like It Is) (Stacey Shiflett)}

\index[FACEBOOK]{JUST BAPTIST OUTLINESS!Stacey Shiflett - Psalm 16:6!2020/04/15}

\noindent \textbf{Introduction: } Let’s look at a few key words in this verse:
\begin{compactenum}[1.][8]
    \item The Lines - a cord, rope, territory, band, company, a rope, cord, a measuring-cord or line, a measured portion, lot, part, region
    \item Fallen unto me – to be offered, to fall into the hands of, to make the lot fall, assign by lot, apportion by lot
    \item In pleasant places - pleasant, delightful, sweet, lovely, agreeable, delightful, beautiful
    \item I have a goodly heritage - possession, property, inheritance\\
\end{compactenum}
David is referring to the inheritance that God had given the nation of Israel in the land of Canaan.
In other words, what David was saying was this: “God has been good to give me a goodly heritage. I have walked around it and surveyed the boundaries, the property lines, the existence of the landmarks, and I like it like it is.”
I want to preach this morning a message entitled: I Like It Like It Is!\\

\noindent \textbf{Conclusion:} So why do I like it like it is?  Why am I satisfied to live within the lines that have fallen to me?
So why is it pleasant and goodly?
Because of:\\
\begin{compactenum}[1.]
    \item I’m not looking to re-survey my heritage.
    \item I’m not looking to move the ancient landmarks.
    \item I’m not looking to redraw the perimeter.
    \item I’m not putting up a “For Sale” sign and moving somewhere else.
    \item I’m not looking for a new heritage or a better plot of land.\\
\end{compactenum}
No – I have to say with David. “The lines are fallen unto me in pleasant places; yea, I have a goodly heritage.”  I have looked it over from one end to the other, and I LIKE IT LIKE IT IS!
You ask me – what is it about the lines that have fallen to you that makes it so pleasant; so goodly??\\
\begin{compactenum}[I.][8]
    \item The \textbf{Distance from Egypt} – One of the things I love about my goodly heritage is how far it is away from Egypt.
When God delivered the nation of Israel, he took them out of Egypt, through the Red Sea, across the wilderness and over the Jordan River.
I like the fact that the lines that have fallen to me are away from the land of bondage.
I’m grateful that the lines that have fallen to me are out of sight from the slavery and pain of Egypt.
It is a pleasant place because when I look out the window of my new inheritance, I don’t have to see the pyramids and the palaces of the wicked.
    \item The \textbf{Deliverance from my Enemy} – As long as I stay where God put me, and as long as I enjoy the lines that have fallen to me, the enemy can’t touch me!
Exodus 23:31 And I will set thy bounds from the Red sea even unto the sea of the Philistines, and from the desert unto the river: for I will deliver the inhabitants of the land into your hand; and thou shalt drive them out before thee.
Deuteronomy 7:2  And when the LORD thy God shall deliver them before thee; thou shalt smite them, and utterly destroy them; thou shalt make no covenant with them, nor shew mercy unto them:
Deuteronomy 7:23 But the LORD thy God shall deliver them unto thee, and shall destroy them with a mighty destruction, until they be destroyed.
Deuteronomy 7:24 And he shall deliver their kings into thine hand, and thou shalt destroy their name from under heaven: there shall no man be able to stand before thee, until thou have destroyed them.
    \item The \textbf{Dividends that I Enjoy} – God described Canaan as a “land flowing with milk and honey” in Exodus 3:8
And sure enough – He kept His word!
Deuteronomy 26:9 And he hath brought us into this place, and hath given us this land, even a land that floweth with milk and honey.
It’s interesting to me that milk and honey both are used to describe several things.
These things are what makes the heritage so goodly and pleasant!\\
    \begin{compactenum}[A.][8]
        \item \textbf{The Precepts of God}
Psalms 119:1035 How sweet are thy words unto my taste! yea, sweeter than honey to my mouth!
1 Peter 2:2  As newborn babes, desire the sincere milk of the word, that ye may grow thereby:
How blessed we are to have access to the heart and mind of God that is revealed to us through His word!
I choose to trust Him and believe His word.
ILLUSTRATION: The conversation I had yesterday on the plane with the engineer from South Africa.
I’m grateful for the exposure I’ve had to the milk and honey of God’s inspired, infallible, inerrant Word!!!
        \item \textbf{The Provision of God}
Deuteronomy 32:12 So the LORD alone did lead him, and there was no strange god with him.  He made him ride on the high places of the earth, that he might eat the increase of the fields; and he made him to suck honey out of the rock, and oil out of the flinty rock;  Butter of kine, and milk of sheep, with fat of lambs, and rams of the breed of Bashan, and goats, with the fat of kidneys of wheat; and thou didst drink the pure blood of the grape.
        \item \textbf{The Path of God}
The Bible is clear – the path of the wicked is difficult.
Proverbs 13:15   …the way of transgressors is hard.
Notice what Solomon told his son about living a life in the wisdom of God. He compared it to honey.
Proverbs 24:13 My son, eat thou honey, because it is good; and the honeycomb, which is sweet to thy taste:  So shall the knowledge of wisdom be unto thy soul: when thou hast found it, then there shall be a reward, and thy expectation shall not be cut off.
Living within the lines of my goodly heritage will be very rewarding.
The godly wisdom of walking in His ways will bring life-long blessing and prosperity.
Notice – thy expectation will not be cut off.
The dividends of living God’s way is the ultimate life.\\
    \end{compactenum}
\end{compactenum}

\begin{compactenum}[I.][8]
    \item The \textbf{Distance from Egypt} – I don’t want to ever go back there!
    \item The \textbf{Deliverance from my Enemy} – I need God to help me fight those battles!
    \item The \textbf{Dividends that I Enjoy} – they make it pleasant and goodly to me.\\
\end{compactenum}

\noindent I don’t want to live without His Precepts, His Provision, and His Path
