\section{Psalm 23 Outlines}

\subsection{My Outlines}

\subsubsection{My Shepherd Gives Me}

\index[speaker]{Keith Anthony!Psalm 023 (My Shepherd Gives Me)}
\index[series]{Psalms (Keith Anthony)!Psalm 023 (My Shepherd Gives Me)}
\index[date]{2016/06/29!Psalm 023 (My Shepherd Gives Me) (Keith Anthony)}

\begin{compactenum}[I.]
    \item \textbf{Provision} \index[scripture]{Psalms!Psa 023:01}(Psa 23:1)
    \item \textbf{Pastures} \index[scripture]{Psalms!Psa 023:02}(Psa 23:2)
    \item \textbf{Paths} \index[scripture]{Psalms!Psa 023:03}(Psa 23:3)
    \item \textbf{Protection} \index[scripture]{Psalms!Psa 023:04}(Psa 23:4)
    \item \textbf{Presence} \index[scripture]{Psalms!Psa 023:05}(Psa 23:5)
    \item A \textbf{Prepared} Table \index[scripture]{Psalms!Psa 023:05}(Psa 23:5)
    \item \textbf{Preservation} \index[scripture]{Psalms!Psa 023:06}(Psa 23:6)
\end{compactenum}

\subsubsection{I Shall Not Want}

\index[speaker]{Keith Anthony!Psalm 023 (I Shall Not Want)}
\index[series]{Psalms (Keith Anthony)!Psalm 023 (I Shall Not Want)}
\index[date]{2018/0520/06!Psalm 023 (I Shall Not Want) (Keith Anthony)}
\begin{compactenum}[I.]
    \item \textbf{Still Waters} \index[scripture]{Psalms!Psa 023:02}(Psa 23:2)
    \item \textbf{Serene Pastures} \index[scripture]{Psalms!Psa 023:03}(Psa 23:3)
    \item \textbf{Restored Soul} \index[scripture]{Psalms!Psa 023:03}(Psa 23:3)
    \item \textbf{Supporting Staff} \index[scripture]{Psalms!Psa 023:04}(Psa 23:4)
    \item \textbf{Set Table} \index[scripture]{Psalms!Psa 023:05}(Psa 23:5)
    \item \textbf{Sure Goodness} \index[scripture]{Psalms!Psa 023:06}(Psa 23:6)
    \item \textbf{Certain Mercy} \index[scripture]{Psalms!Psa 023:06}(Psa 23:6)
\end{compactenum}


\subsubsection{The Shepherd in the Wilderness}

\index[speaker]{Keith Anthony!Psalm 023 (The Shepherd in the Wilderness)}
\index[series]{Psalms (Keith Anthony)!Psalm 023 (The Shepherd in the Wilderness)}
\index[date]{2017/08/06!Psalm 023 (The Shepherd in the Wilderness) (Keith Anthony)}

\begin{compactenum}[I.]
    \item The \textbf{Ruggedness} -- rugged wilderness covers much of Israel. The two most prominent deserts are the Judea Wilderness running along the eastern edge of the Judea Mountains, and the Negev lying in southern Israel. Israel's wilderness abounds with rocks, hills, and canyons. The climate is one of extremes swith scorching hot temperatures by day turn to near-freezing temperatures at night. Though it receives little rainfall, the wilderness can sustain the flocks of nomadic shepherds. The Negev desert where David would have grazed his sheep is a far cry from the abundantly grassy meadows of Sunday school paintings. It is a desert after all. From time to time our bus would pass by a hill covered in sparse grass and we would see Bedouin shepherds grazing their flocks on it. Then miles would pass, miles of hills covered in nothing but dust and rock, before another hill would appear which sported the tiny patches of green.
	\item The \textbf{Rocks} -- Westerners imagine lush, green meadows when they hear the word ``pasture,'' but ``green pastures'' in Israel actually look like rocky, barren hillsides. Scattered amidst the rocks are blades of grass. Where a drop of rain fell or dew collected beneath a rock, a single tuft of grass can sprout up. %\index[scripture]{Psalms!Psalm 023:01}(Psalm 23:1)
    \item The \textbf{Route} -- When you look at the hills in the Negev, you see what looks like ``terraces'' on them.  These are the grazing paths where the shepherds have led their flocks.
    \item The \textbf{Rain} -- There hardly ever is rain in the Negev desert. Instead, sometimes a slightly damp breeze blows in from the sea to the west.  From these breezes, moisture condenses on the hills allowing grass to grow.  What about the still waters? As other travelers could tell you, the climate in Israel is typically hot and dry, but my group had the opportunity to visit during the brief rainy season. It rained almost every day, soaking us to the bone and pushing our cheap tourist umbrellas to their limits. During this season, the wadis are suddenly filled with water. A wadi is a stream bed in the desert that is dry all year `round until the rainy season comes. During this season, all the water that falls on the hills is channeled down into the wadis and they burst violently into life, rushing angrily down the hills into the Dead Sea.  If a shepherd led his sheep to drink in a wadi, they would be dragged in and under. They would be carried along by the merciless current and smashed repeatedly against the rocks until their drowned and broken bodies reached the wadi's destination. ``A good shepherd is a shepherd who can find still waters in the midst of a desert, from which his sheep can drink in safety.''
    \item The \textbf{Rod} -- The shepherd has a rod and a staff. These are used mainly to put wayward sheep back on the correct path. The wrong path (1) will not have enough food, and (2) will be a place of predators.
    \item The \textbf{Recognition} -- Over time, sheep in a flock will comes to recognize the voice of their shepherd. Another aspect of recognition is that the shepherd is aware that the sheep he is watching belong to someone else!
\end{compactenum}

