\section{Psalm 1 Outlines}

\subsection{My Outlines}

\subsubsection{A Psalm of Comparisons}
\textbf{Introduction: }Psalm 1 compares the path of the righteous and the paths of the ungodly:
\index[speaker]{Keith Anthony!Psalm 001 (A Psalm of Comparisons)}
\index[series]{Psalms (Keith Anthony)!Psalm 001 (A Psalm of Comparisons)}
\index[date]{2015/08/24!Psalm 001 (A Psalm of Comparisons) (Keith Anthony)}
\begin{compactenum}[I.]
    \item A \textbf{Downward Cycle} \index[scripture]{Psalms!Psa 001:01}(Psa 1:1)
    \item A \textbf{Dialobical Counsel} \index[scripture]{Psalms!Psa 001:01}(Psa 1:1)
    \item \textbf{Diligent Consideration} \index[scripture]{Psalms!Psa 001:02}(Psa 1:2)
    \item A \textbf{Different Course} \index[scripture]{Psalms!Psa 001:02}(Psa 1:2)
    \item \textbf{Driven Chaff} \index[scripture]{Psalms!Psa 001:04}(Psa 1:4)
    \item \textbf{Distinguishing Characteristics}  \index[scripture]{Psalms!Psa 001:04}(Psa 1:4)
    \item A \textbf{Delivered Congregation} \index[scripture]{Psalms!Psa 001:05}(Psa 1:5)
    \item A \textbf{Definite Conclusion} \index[scripture]{Psalms!Psa 001:06}(Psa 1:6)
\end{compactenum}

\subsubsection{The Psalm 1 Man}
Psalm 1 provides a description of a different sort of man.  The man seeks God.  He seeks truth and righteousness.  He is radically different from the man of the world, and the man of the flesh, and the man who seeks the Devil. The Psalm 1 man: %\footnote{05 June 2015, Prepared for Lebanon Baptist Temple preaching class}
\index[speaker]{Keith Anthony!Psalm 001 (The Psalm 1 Man)}
\index[series]{Psalms (Keith Anthony)!Psalm 001 (The Psalm 1 Man)}
\index[date]{2015/06/05!Psalm 001 (The Psalm 1 Man) (Keith Anthony)}


\index[LOCATION]{Greene County Adult Detention Center!2022/01/11!Tuesday Night}

\begin{compactenum}[I.]
    \item \fcolorbox{bone}{yellow}{\textbf{Shuns Fools}} \index[scripture]{Psalms!Psa 001:01}(Psa 1:1) The word fool is used 66 times in the King James. The word ``fools'' is found another 42 times. ``Foolish'' is found 52 times! Foolishly, 12 times; foolishness, 20 times. That's 199 times that variants of the word are found (78 times in Proverbs).How about:
    \begin{compactenum}[A.]
		\item Psalm 14:1: The fool hath said in his heart, There is no God. They are corrupt, they have done abominable works, there is none that doeth good.
		\item Psalm 74:18:O LORD, and that the foolish people have blasphemed thy name.
		\item Proverb 27:3:  Though thou shouldest bray a fool in a mortar among wheat with a pestle, yet will not his foolishness depart from him. (stuck on folly)
	\end{compactenum}
    \item \fcolorbox{bone}{yellow}{Has \textbf{Select Friends}} \index[scripture]{Psalms!Psa 001:01}(Psa 1:1)
    \begin{compactenum}[A.]
    	\item 1 Corinthians 15:33 Be not deceived: evil communications corrupt good manners.
    	\item Proverb 12;26 The righteous is more excellent than his neighbour: but the way of the wicked seduceth them.
    	\item Proverb 13:20 He that walketh with wise men shall be wise: but a companion of fools shall be destroyed.
    	\item Proverb 20:19 He that goeth about as a talebearer revealeth secrets: therefore meddle not with him that flattereth with his lips.
    	\item Proverb 22:24-25 Make no friendship with an angry man; and with a furious man thou shalt not go: 25 Lest thou learn his ways, and get a snare to thy soul.
    	\item Proverb 24:6 For by wise counsel thou shalt make thy war: and in multitude of counsellors there is safety.
    	\item 2 Corinthians 6:14 Be ye not unequally yoked together with unbelievers: for what fellowship hath righteousness with unrighteousness? and what communion hath light with darkness?
    \end{compactenum}
	\item \fcolorbox{bone}{yellow}{Eats \textbf{Spiritual Food}} \index[scripture]{Psalms!Psa 001:02}(Psa 1:2) - Spiritual food is the blessings of God. It is typified by manna in the Old testament. Obedience is spiritual food. Doctrine is spiritual food. Worship is spiritual food. Prayer is spiritual food. Some verses:
    \begin{compactenum}[A.]
		\item 1 Corinthians 10:1-4 Moreover, brethren, I would not that ye should be ignorant, how that all our fathers were under the cloud, and all passed through the sea; 2 And were all baptized unto Moses in the cloud and in the sea; 3 And did all eat the same spiritual meat; 4 And did all drink the same spiritual drink: for they drank of that spiritual Rock that followed them: and that Rock was Christ.
		\item 1 Peter 2:2 As newborn babes, desire the sincere milk of the word, that ye may grow thereby:
		\item Hebrews 5:12-14 For when for the time ye ought to be teachers, ye have need that one teach you again which be the first principles of the oracles of God; and are become such as have need of milk, and not of strong meat. 13 For every one that useth milk is unskilful in the word of righteousness: for he is a babe. 14 But strong meat belongeth to them that are of full age, even those who by reason of use have their senses exercised to discern both good and evil.
		\item Jeremiah 3:15 And I will give you pastors according to mine heart, which shall feed you with knowledge and understanding.
		\item John 6:51 I am the living bread which came down from heaven: if any man eat of this bread, he shall live for ever: and the bread that I will give is my flesh, which I will give for the life of the world.
		\item Revealtion 2:7 He that hath an ear, let him hear what the Spirit saith unto the churches; To him that overcometh will I give to eat of the tree of life, which is in the midst of the paradise of God.
    \end{compactenum}
    \item \fcolorbox{bone}{yellow}{Has \textbf{Special Fellowship}} \index[scripture]{Psalms!Psa 001:02}(Psa 1:2) with God and with believers and with scripture
    \begin{compactenum}[A.]
    	\item Colossians 3:16 Let the word of Christ dwell in you richly in all wisdom; teaching and admonishing one another in psalms and hymns and spiritual songs, singing with grace in your hearts to the Lord.
		\item Romans 1:12 That is, that I may be comforted together with you by the mutual faith both of you and me.
		\item Hebrews 10:24-25 And let us consider one another to provoke unto love and to good works: 25 Not forsaking the assembling of ourselves together, as the manner of some is; but exhorting one another: and so much the more, as ye see the day approaching.
    \end{compactenum}
    \item \fcolorbox{bone}{yellow}{He Can \textbf{Sense Falsehood(s)} }
        \begin{compactenum}[A.]
        	\item 1 Chronicles 12:32 And of the children of Issachar, which were men that had understanding of the times, to know what Israel ought to do; the heads of them were two hundred; and all their brethren were at their commandment.
        	\item Psalm 119:105 Thy word is a lamp unto my feet, and a light unto my path.
        	\item Hebrews 5:15 But strong meat belongeth to them that are of full age, even those who by reason of use have their senses exercised to discern both good and evil.
           \end{compactenum}
     \item \fcolorbox{bone}{yellow}{He \textbf{Sees the Future}} Bible, carefully studied and rightly divided, records the essential human history and clearly lays out the future
    \begin{compactenum}[A.]
    	\item Amos 3:7 Surely the Lord GOD will do nothing, but he revealeth his secret unto his servants the prophets.
    	\item Acts 1:7-8 And he said unto them, It is not for you to know the times or the seasons, which the Father hath put in his own power. 8 But ye shall receive power, after that the Holy Ghost is come upon you: and ye shall be witnesses unto me both in Jerusalem, and in all Judæa, and in Samaria, and unto the uttermost part of the earth.
    \end{compactenum}
    \item \fcolorbox{bone}{yellow}{Has his \textbf{Sins Forgiven}} (All)
    \begin{compactenum}[A.]
    	\item Isaiah 1:18  Come now, and let us reason together, saith the LORD: though your sins be as scarlet, they shall be as white as snow; though they be red like crimson, they shall be as wool.
    	\item Isaiah 55:7  Let the wicked forsake his way, and the unrighteous man his thoughts: and let him return unto the LORD, and he will have mercy upon him; and to our God, for he will abundantly pardon.
    	\item John 3:1-17 For God so loved the world, that he gave his only begotten Son, that whosoever believeth in him should not perish, but have everlasting life. 17 For God sent not his Son into the world to condemn the world; but that the world through him might be saved.
    	\item Romans 6:23 For the wages of sin is death; but the gift of God is eternal life through Jesus Christ our Lord.
    	\item Romans 8:1 There is therefore now no condemnation to them which are in Christ Jesus, who walk not after the flesh, but after the Spirit.
		\item 1 John 1:9 If we confess our sins, he is faithful and just to forgive us our sins, and to cleanse us from all unrighteousness.
		\item 1 John 2:12 I write unto you, little children, because your sins are forgiven you for his name’s sake.
    \end{compactenum}
    \item \fcolorbox{bone}{yellow}{Has a \textbf{Spectacular \& Secure Finish}} \index[scripture]{Psalms!Psa 001:06}(Psa 1:6)
    \begin{compactenum}[A.]
		\item John 3:14-16 And as Moses lifted up the serpent in the wilderness, even so must the Son of man be lifted up: 15 That whosoever believeth in him should not perish, but have eternal life.
16 ¶ For God so loved the world, that he gave his only begotten Son, that whosoever believeth in him should not perish, but have everlasting life.
		\item Romans 6:23 For the wages of sin is death; but the gift of God is eternal life through Jesus Christ our Lord.
		\item John 4:14  But whosoever drinketh of the water that I shall give him shall never thirst; but the water that I shall give him shall be in him a well of water springing up into everlasting life.
		\item 1 John 2:25 And this is the promise that he hath promised us, even eternal life.
		\item Titus 3:3-7 For we ourselves also were sometimes foolish, disobedient, deceived, serving divers lusts and pleasures, living in malice and envy, hateful, and hating one another. 4 But after that the kindness and love of God our Saviour toward man appeared, 5 Not by works of righteousness which we have done, but according to his mercy he saved us, by the washing of regeneration, and renewing of the Holy Ghost; 6 Which he shed on us abundantly through Jesus Christ our Saviour; 7 That being justified by his grace, we should be made heirs according to the hope of eternal life. 
    \end{compactenum}
    \item Exercises \textbf{Simple Faith} (All)
    \begin{compactenum}[A.]
		\item Matthew 18:3 And said, Verily I say unto you, Except ye be converted, and become as little children, ye shall not enter into the kingdom of heaven
		\item Luke 18:17 Verily I say unto you, Whosoever shall not receive the kingdom of God as a little child shall in no wise enter therein
		\item Hebrews 11:6 ut without faith it is impossible to please him: for he that cometh to God must believe that he is, and that he is a rewarder of them that diligently seek him.
		\item Romans 10:17  So then faith cometh by hearing, and hearing by the word of God.
		\item Romans 1:17  For therein is the righteousness of God revealed from faith to faith: as it is written, The just shall live by faith.
    \end{compactenum}
\end{compactenum}

\subsubsection{A Cosmic Comparison}
Psalm 1 contrasts an ungodly man with one who seeks God Almighty. There are numerous differences.  Among them: %\footnote{04 June 2015, Prepared for Lebanon Baptist Temple preaching class}
\index[speaker]{Keith Anthony!Psalm 001 (A Cosmic Comparison)}
\index[series]{Psalms (Keith Anthony)!Psalm 001 (A Cosmic Comparison)}
\index[date]{2015/06/04!Psalm 001 (A Cosmic Comparison) (Keith Anthony)}
\begin{compactenum}[I.]
    \item They have Different \textbf{Objectives}
    \item They have Different \textbf{Orientations}
    \item They have Different \textbf{Obsessions}
    \item They have Different \textbf{Orientations}
    \item They have Different \textbf{Obstacles}
    \item They have Different \textbf{Outcomes}
\end{compactenum}

\subsubsection{Road-markers on the Road to Scorn}
I know a little bit about this, as does any Christian who has lived for more than a few years. Psalm 1 talks about the seat of the scornful.  Almost any Christian or every Christian has been abused by other Christians, mistreated by ministers, misunderstood, etc. Almost every Christian has been at one time or another on the wrong side of an apparent double-standard. These  are all dangerous place to be, as the response or rather how one decides to respond will make a world of difference. If you can picture Christianity as a highway, then there is also another parallel road, probably with a slow lane and a high-speed lane. At any point a Christian can exit off the Christian highway and get on this other road, going the opposite direction. Sometimes it is tough to recognize that you've done so. In Psalm 1, the destinations of these two roads are made known.  The place of blessing and the seat of the scornful. So, I got to thinking more about this road to this seat of the scornful.  What does the path look like?  What are the road-markers? This is just case you are seeing some of these road-markers of late.  Maybe you are on this road to the seat of the scornful. Maybe there are a few road signs that will tell you that you are: 
%\footnote{16 June 2015, Prepared for Lebanon Baptist Temple preaching class}
\index[speaker]{Keith Anthony!Psalm 001 (Road-markers on the Road to Scorn)}
\index[series]{Psalms (Keith Anthony)!Psalm 001 (Road-markers on the Road to Scorn)}
\index[date]{2015/06/16!Psalm 001 (Road-markers on the Road to Scorn) (Keith Anthony)}
\begin{compactenum}[I.]
    \item Not \textbf{Recognizing Blessings}
    \item \textbf{Reviling the Brethren}
    \item Not \textbf{Reading the Book}
    \item \textbf{Revelling in Bitterness}
    \item Not \textbf{Remembering the Burdens}
    \item Not \textbf{Regarding the Body}
    \item Not Carrying the \textbf{Burdens of Believers}
\end{compactenum}

\subsubsection{The Ungodly Man}
Psalm 1 provides insight into the ungodly man. The word ``ungodly'' is found 27 times in 24 verses in scripture, notably 4 times in Jude 15. Here is used in the corporate sense, as in ungodly people. Usages of the word: %\footnote{07 June 2016, Keith Anthony}
\index[speaker]{Keith Anthony!Psalm 001 (The Ungodly Man}
\index[series]{Psalms (Keith Anthony)!Psalm 001 (The Ungodly Man}
\index[date]{2016/06/07!Psalm 001 (The Ungodly Man (Keith Anthony)}
\begin{compactenum}[I.][8]
	\item ungodly \textbf{man} \index[scripture]{Psalms!Psa 001:01}  \index[scripture]{Psalms!Psa 001:04}  \index[scripture]{Psalms!Psa 001:05}  \index[scripture]{Psalms!Psa 003:07}  \index[scripture]{Psalms!Psa 018:04}  \index[scripture]{Proverbs!Pro 16:27} \index[scripture]{Romans!Rom 04:04} (Psa 1:1, 1:4, 1:5, 3:7, 18:4, Pro 16:27, Rom 4:4)
	\item ungoldy \textbf{men} \index[scripture]{2 Samuel!2Sam 22:05} \index[scripture]{2 Chronicles!2Chr 19:02} (2Sam 22:5, 2Chr 19:2, Job 16:11, Job 34:18, Psa 1:6, Psa 73:12, 1Tim 1:9, 1Pet 4:18, 2Pet 2:5, 2Pet 2:6, 2Pet 2:7, Jude 1:4, Jude 1:15)
	  \index[scripture]{Job!Job 16:11}\index[scripture]{Job!Job 34:18} \index[scripture]{Psalms!Psa 001:06} \index[scripture]{Psalms!Psa 073:12}\index[scripture]{1 Timothy!1Tim 01:09} \index[scripture]{1 Peter!1Pet 04:18}\index[scripture]{2 Peter!2Pet 02:05}\index[scripture]{2 Peter!2Pet 02:06}\index[scripture]{2 Peter!2Pet 02:07}\index[scripture]{Jude!Jude 01:15}
	\item ungodly \textbf{nation} \index[scripture]{Psalms!Psa 043:01} (Psa 43:1)
	\item ungodly \textbf{witness} \index[scripture]{Proverbs!Pro 19:28} (Pro 19:28)
	\item ungodly \textbf{deeds} \index[scripture]{Jude!Jude 01:15} (Jude 1:15)
	\item ungodly \textbf{actions} \index[scripture]{Jude!Jude 01:15} (Jude 1:15)
	\item ungodly \textbf{lusts} \index[scripture]{Jude!Jude 01:18} (Jude 1:18)
\end{compactenum}

