\section{Psalm 24 Ruckman Comments}

\subsection{Psalm 24:1}
The Church Age is followed by the Advent. So the Lord has chosen for the Advent a coronation Psalm. “The King of glory” in the passage is one Man and one Man only; it is the Lord Jesus Christ, the anointed Messiah (the “Christos”) of Israel. “The earth is the LORD’s and the fulness thereof” is applied by Paul in a spiritual sense in 1 Corinthians 10:26, but this “original” is literal and must be taken as such. “The hill of the LORD” (vs. 3) is mentioned again as it is mentioned in the Millennial passage in Psalm 2:6. The “holy place” (vs. 3) is mentioned again as it is mentioned in Psalm 15:1–2, and the WORKS and FAITH salvation shows up again, exactly as it does in Psalm 15. In vain do the apostates at Liberty University (Kroll) try to line the Psalm up with the Pauline Epistles and Taylor’s “Living Catastrophe.” They don’t line up, no matter what they try. Everything is tried.
1. The passage is “describing the FRUITS of the regenerated life.’’
2. The passage is “suggesting moral requirements for pleasing God.’’
3. The passage is giving the “essential qualifications for a saved person’’ who wishes to “serve” God; so forth and so on.
Nothing “jives.” Nothing fits. Nothing is created but confusion without form and void, and darkness upon the face of the deep. It is said of the generation that receives the King of Glory into Jerusalem: “This is the generation” (vs. 6). It is not any generation between A.D. 33 and 1948. Compare verse 1 with Zechariah 14:9. 



\subsection{Psalm 24:3}

Verse 3 should be compared to Isaiah 57:13. “For he hath founded it upon the seas ... the floods” (vs. 2). Panic. All of the commentators, without a single exception, drive the verse back to Noah’s flood (and then have to take the “s” off of it), or drive it to Genesis chapter 1 where the “dry land” appears in the MIDDLE of the seas (Gen. 1:9--10). All of the ducking, dodging, twisting, and turning is because the original earth was “standing out of the water and in the water” (2 Pet. 3:5--6), and this was neither the earth of Genesis 1:9--10, nor the one that Noah dealt with. In the original creation (Gen. 1:1) the “holy hill” and the “holy place” were right THERE until the earth became “without form and void,” and the earth “that then was, being overflowed with water, perished” (2 Pet. 3:5–6). The modern apostates (RV, RSV, NRSV, ASV, NASV, NIV, and NKJV) leave the AV text in fair condition because they figure it is “figurative” anyway; so no one needs to alter it. However, when asked to comment on it, they defect immediately. 



\subsection{Psalm 24:6}

Note, for the tenth time, the word “SELAH” is placed in order to warn the reader that he is in a Second Advent context (vs. 6). “O ye gates...ye everlasting doors” refers to more than the Eastern Gate where the Lord Jesus Christ will enter (Ezek. 43:4; Zech. 14:4) and to more than the “doors” of a tabernacle or Millennial temple. These are the GATES and DOORS that (like the WINDOWS of 2 Kings 7:2, 19 and Song of Sol. 2:9) are about two hundred-fifty million light years over your head. They are pictured in Nehemiah chapters 2--3 as prefigured in earthly Jerusalem. If a scientist or astronomer were to locate them he would call them something else (there is no cure for a stupid man who is trying to justify his sins). “The King of glory” comes into these gates at His ascension, victoriously bringing “captivity captive” (Eph. 4:8), after publically putting the devil to an “open shame” (Heb. 6:6) by humiliating him and his “powers” through the cross (Col. 2:15; John 16:11). Zion had a halleuia “shouting spell” when the King of the Jews returned home to the Ivory Palaces after thirty-three and one half years of poverty, persecution, harassment, ridicule, slander, pain, and agony.

\subsection{Psalm 24:9, 10}
“The King of glory” will “come in” again to earthly Jerusalem through the same gate that He went out the night before He was crucified. He will cross the brook Kidron (John 18:1) from the Mount of Olives (Zech. 14:1–6; Acts 1:11–12), and enter Jerusalem as “KING OF KINGS AND LORD OF LORDS” (Rev. 19:16). He will take the route He took on ``a colt, the foal of an ass'' (Zech. 9:9; Gen. 49:11) but this time it will be on a thoroughbred WHITE Arabian charger (Rev. 19:11, 14:19–20), dripping with the blood (Gen. 49:11; Isa. 63:1–6; Ps. 68:23; Rev. 14:19–20) of secular humanists, pragmatic anarchists, Roman Catholics, Moslems, ecologists, political activists, Satanists, and the “PEACEMAKERS”—the UN, the IRA, the PLO, the popes: the whole godless, hellish, damnable, depraved MESS. “Who is this King of glory?” (vss. 8, l0). It is “the LORD of hosts...Selah!” (vs. 10). He is a Shepherd-King exactly as the Holy Spirit described the matter in Zechariah 13:7. And wouldn’t these apostate Fundamentalists have a fit if that white Arabian stallion had one long horn protruding right from between his eyes!? Wouldn’t that tie the rag on the bush!