\section{Psalm 4 Outlines}

\subsection{My Outlines}

\subsubsection{Confidence in God}

\index[speaker]{Keith Anthony!Psalm 004 (Confidence in God)}
\index[series]{Psalms (Keith Anthony)!Psalm 004 (Confidence in God)}
\index[date]{unknown!Psalm 004 (Confidence in God) (Keith Anthony)}
\begin{compactenum}[I.]
    \item \textbf{Consideration of God's Enemies} \index[scripture]{Psalms!Psa 004:01}(Psa 4:1)
    \item \textbf{Call to the Faithful One} \index[scripture]{Psalms!Psa 004:01}(Psa 4:1)
    \item \textbf{Confidence in God's Way} \index[scripture]{Psalms!Psa 004:01}(Psa 4:1)
    \item \textbf{Contentment in Heart} \index[scripture]{Psalms!Psa 004:07}(Psa 4:7)
    \item \textbf{Countenance Provided} \index[scripture]{Psalms!Psa 004:06}(Psa 4:6)
    \item \textbf{Confirmation of Presence} \index[scripture]{Psalms!Psa 004:08}(Psa 4:8)
    \item \textbf{Calmness and Peace} \index[scripture]{Psalms!Psa 004:08}(Psa 4:8)
\end{compactenum}

\subsubsection{The Ministry of Lies}

\index[speaker]{Keith Anthony!Psalm 004 (The Ministry of Lies)}
\index[series]{Psalms (Keith Anthony)!Psalm 004 (The Ministry of Lies)}
\index[date]{Keith Anthony!Psalm 004 (The Ministry of Lies) (Keith Anthony)}
\begin{compactenum}[I.]
	\item  \textbf{Insincere Boldness} -- Do you take a hard stand against something, but in  the details, one could see small compromises on the same issue
	\item \textbf{Imperfect Book} -- Do you really have a perfect book? Do you actually believe  the WORDS that it says?
	\item \textbf{Impure Bride} -- what ``little sins'' of convenience do you overlook (most likely, non-Christians are not overlooking them)
	\item \textbf{Insincere Brethren} -- Don't pretend to care, if you don't $\hdots$  don't say you pray or will pray when you don't or won't $\hdots$ And why do you not care  anyway?
	\item \textbf{Inordinate Bonds} - (Ezekiel 23:11) Who or what are you beholden to? Who are you secretly trying to be like?
	\item \textbf{Inconsistent Beliefs} -- How much or your beliefs actually are not scriptural? And how would you react when someone showed you?
	\item \textbf{Invisible Blessings} -- if you say you are a Christian, who are you being a blessing to?
	\item A\textbf{(Mis)Interpreted Bible} -- Do  you REALLY understand the Bible, or just take the word of the guy in the pulpit?
\end{compactenum}

