\section{Psalm 19 Comments}

\subsection{Numeric Nuggets}
\textbf{13:} Verse 1 has 13 words.  The 13-letter word ``trangression'' shows up in verse 13.

\subsection{Psalm 19 Introduction}

Seven items are listed in Psalm 19, as a logical follow-on to the revelation in the early part of the psalm (identified by the phrase ``of the Lord'', found in verses 7, 8, and 9, each at words number 3 and 13). These are the things that are doing the speaking in the psalm. But we must add one more, the heavens:\\
\begin{compactenum}
	\item The \textbf{heavens}  (verse 1)
	\item The \textbf{law} of the Lord (verse 7)
	\item The \textbf{testimony} of the Lord (verse 7)
	\item The \textbf{statutes} of the Lord (verse 8)
	\item The \textbf{commandments} of the Lord (verse 8)
	\item The \textbf{fear} of the Lord (verse 9)
	\item The \textbf{judgments} of the Lord (verse 9)	\\
\end{compactenum}
\noindent These point also to Psalm 119, where they are discussed in depth.

\subsection{Numeric Nuggets}
There are thirteen words in Psalm 19:1, suggesting in general, that mankind will rebel against the general revelation of creation. The thirteen-letter word ``transgression'' is used in Psalm 19, notably in verse 13. 

\subsection{Psalm 19:1}
This verse is corrupted in new translations (see Table~\ref{table:CorruptionPsalm-19-1}).
\include{19OT-Psalms/CorruptionAlerts/Psalm-19-1}


\subsection{Psalm 19:12}
The immediate cross-reference that comes to mind is Jeremiah 17:9,10.\footnote{\textbf{Jeremiah 17:9, 10} - The heart is deceitful above all things, and desperately wicked: who can know it? [10] I the LORD search the heart, I try the reins, even to give every man according to his ways, and according to the fruit of his doings.} This, though, is just one of the 44 references to the ``who can'' (both cases) phrase in scripture.

\include{WordsAndPhrasesInScripture/WAPFIS-whoCan}

\subsection{Psalm 19:13}
This verse is corrupted in new translations (see Table~\ref{table:CorruptionPsalm-19-13}).
\include{19OT-Psalms/CorruptionAlerts/Psalm-19-13}

