\section{Psalm 2 Comments}



\subsection{Psalm 2:1, 2}
Modern translations corrupt this verse.\footnote{\textbf{Isaiah 40:17} - All nations before him are as nothing; and they are counted to him less than nothing, and vanity.} But these heathen are everywhere.  The rage. They rule.  They rise up. They mostly reject. They ruin things.  Theses heathen are the ones to whome the gospel is to be preached in Galatians 1:16, 2:9, and 3:8.\footnote{\textbf{Galatians 1:16} - To reveal his Son in me, that I might preach him among the heathen; immediately I conferred not with flesh and blood:}\footnote{\textbf{Galatians 2:9} - And when James, Cephas, and John, who seemed to be pillars, perceived the grace that was given unto me, they gave to me and Barnabas the right hands of fellowship; that we should go unto the heathen, and they unto the circumcision.}\footnote{\textbf{Galatians 3:8} - And the scripture, foreseeing that God would justify the heathen through faith, preached before the gospel unto Abraham, saying, In thee shall all nations be blessed.}\\
\\
\noindent Verses 1 and 2 are used in Acts 4:27 to describe the collection of Pilate, Herod, the Gentiles, Christ-rejecting Israelites, organized religion, and organized politics, to rise up and destroy God's work on Earth.  But this rebellion was only partially fulfilled.\cite{Ruckman1992PsalmsV1} The future focus of united mankind (typified in Genesis 11) will be this rebellion.
\input{19OT-Psalms/CorruptionAlerts/Psalm-2-1}



\subsection{Psalm 2:3}
There are some sort of ``bands'' and ``cords'' that are currently preventing the conclusion of this rage. Something like this is described in Isaiah 30:28 and Matthew 13:30. Something like this is described in 2 Thessalonians 2:6.\footnote{\textbf{Isaiah 30:28} - And his breath, as an overflowing stream, shall reach to the midst of the neck, to sift the nations with the sieve of vanity: and there shall be a bridle in the jaws of the people, causing them to err.}\footnote{\textbf{Matthew 13:30} - The field is the world; the good seed are the children of the kingdom; but the tares are the children of the wicked one;}\footnote{\textbf{2 Thessalonians 2:6} - And now ye know what withholdeth that he might be revealed in his time.} \cite{Ruckman1992PsalmsV1}
