\section{Psalm 24 Comments}

\subsection{Numeric Nuggets}
\textbf{4:} The phrase ``king of glory'' is used 4 times (in verses 7, 8, 9, and 10).\\
\\
\textbf{5:} The phrase ``King of glory'' is found 5 times. With 5 being the number of death, this hints at a substitutionary death. All five instances occur after the first of two uses of ``Selah.''\\
\\
\textbf{13:} Verses 1, 5, and 10 have 13 unique words. The 13-letter word ``righteousness'' is used in the chapter.


\subsection{Psalm 24:1}
Verse 1 is a point of theological departure, if one addresses the question, Is the earth the lord's and the fulness thereof?  Obviously, now, if the answer is no, or if it actually was, the Lord would be a spectacularly ineffective ruler in righteousness. The earth is the Lord's, but it is temporarily being ruled by someone else. This is to change.


\subsection{Psalm 24:8-10}

So, who exactly is the ``King of Glory"? Verse 10 answers the question -- the LORD of hosts.  But, for further enlightenment, scripture provides more answers to the ``who is'' question:
\begin{compactenum}
	\item Exodus 15:11 -- Tells us that the ``who is'' is glorious in holiness, fearful in praises, doing wonders,
	\item 1 Samuel 22:4 -- Tells us that the ``who is'' worthy to be praised.
	\item Isaiah 63:1 -- Tells us that the ``who is''  is this that cometh from Edom, with dyed garments from Bozrah? this that is glorious in his apparel, travelling in the greatness of his strength? I that speak in righteousness, mighty to save.
	\item 2 Corinthians 4:4 -- Tells us that the ``who is'' is the image of God, should shine unto them.
	\item Colossians 1:18-20 -- Tells us that the ``who is'' s the beginning, the firstborn from the dead; that in all things he might have the preeminence. [19] For it pleased the Father that in him should all fulness dwell; [20] And, having made peace through the blood of his cross, by him to reconcile all things unto himself; by him, I say, whether they be things in earth, or things in heaven.
	\item Colossians 3:4 -- Tells us that the ``who is'' is our life.
	\item 1 Timothy 6:15 -- Tells us that the ``who is'' is the blessed and only Potentate, the King of kings, and Lord of lords; 16 Who only hath immortality, dwelling in the light which no man can approach unto; whom no man hath seen, nor can see: to whom be honour and power everlasting. Amen. 
	\item Hebrews 7:16 --Tells us that the ``who is'' is made, not after the law of a carnal commandment, but after the power of an endless life.
	\item Hebrews 7:26 -- Tells us that the ``who is'' is holy, harmless, undefiled, separate from sinners, and made higher than the heavens;
	\item Hebrews 7:28 -- Tells us that the ``who is''  is is consecrated for evermore.
	\item Hebrews 8:1 -- Tells us that the ``who is''  is set on the right hand of the throne of the Majesty in the heavens;
	\item Hebrews 11:27 -- Tells us that the ``who is'' is the invisible but omnipotent God.
	\item 1 Peter 3:22 -- Tells us that the ``who is'' is on the right hand of God; angels and authorities and powers being made subject unto him..
	\item Revelation 5:2 -- Tells us that the ``who is'' is the only one worthy to open the book
\end{compactenum}

Consider the popular song, The Little Boy from the Carpenter Shop:

\begin{verbatim}
He was born in a stable, His [Am]mother a virgin; 
raised in a carpenter shop.
His people were slaves, His parents were poor; 
His friends were a lowly lot.
His chances in life, seemed so slim; why, 
He's expected to be a slave.
But the people in darkness saw light in Him; 
as hope for freedom He gave.

[C]All of the power of [Am]heaven and earth;[F] 
God has invested in[C]Him.
[C]He's to die on the cross, [Am]descend into hell; 
meet the [F]devil, take the keys from [G7]him.
He [F]yielded His life to the [G7]death on the cross; 
cried it's [F]finished and then He [G7]died.
In the [C]regions of hell, the [F]devil celebrated; 
we've [C]destroyed the [G7]King, he [C]cried.

In the [C]midst of the celebration, [Am]footsteps were heard; 
walk-[F]ing the corridors of [C]hell.
Then the [C]shouting stopped, as a [Am]voice rang out; 
a [F]voice as clear as a [G7]bell.
[F]Satan then trembled as he [G7]recognized Him; 
who [F]came to deliver His [G7]own.

Oh, [C]shut and lock the [F]gates he cried; 
don't [C]let Him [G7]ascend to His [C]Throne.
Then the [C]gates swung shut in the [Am]face of our LORD; 
to [F]prove salvation [C]untrue.
But, He [C]shook hell's gates, cried [Am]lift up your heads; 
the [F]King is coming [G7]through.

Then out of the devil's prison house 
came a procession led by our King.
Crying out oh grave, where [F]is thy victory; 
and death where is thy [C]sting?
Who is the [F]King of Glory? 
The LORD GOD ALMIGHTY; that is He.
Who is the King of Glory? 
He's the master of the host of heaven supreme.

[C]Who is the [F]King of Glory? 
He's the one that not even death could [C]stop!
[C]Who [G7]is the King of Glory? 
The Little Boy from the Carpenter [C]Shop[~F~C]
[C]The Little [G7]Boy from the Carpenter [F]Shop![~~C]
\end{verbatim}