\section{Psalm 13 Comments}

\subsection{Numeric Nuggets}
There are thirteen words in verse 6, which speaks of singing unto the Lord in response to his bountiful mercy and grace. There are 13 unique words in verse 6. Refusal to sing is rebellion, or evidence of no new birth.

\subsection{Psalm 13:2}
This question ``how long?'' is asked 4 times in this Psalm, 19 in Psalms, and 61 times in scripture.\footnote{Ryrie points out that the four-fold repetition of \emph{how long} indicates the extremity of David's misery.} The first of these is in Exodus 10:3, with Moses and Aaron asking Pharaoh how long would Pharaoh refuse to humble himself before God.\footnote{\textbf{Exodus 10:3} - And Moses and Aaron came in unto Pharaoh, and said unto him, Thus saith the LORD God of the Hebrews, How long wilt thou refuse to humble thyself before me? let my people go, that they may serve me.} We ought to be happy that the patience of God is longer than ours.


\subsection{Psalm 13:6}
See the references to ``fire and brimstone'' here and in Ezekiel 38:22, Luke 17:29, Revelation 14:10, 20:10, and 21:8. ``Fire and brimstone'' speaks of judgment.\\
\\
I have on occasion witnessed the phenomenon of a supposed Christian staying silent while hymns were sung in a church, for multiple years.  How can this be? I have a new song in my heart, and even if I could not carry a tune, I would lift my voice!   The saints are always singing in scripture! Consider the references to ``new song'' (there are nine references - the number of fruitfulness): Psalm 33:3, 40:3, 98:1, 144:9, 149:1, Isaiah 42:10, Revelation 5:9, and 14:4).